Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-02 causal-bandit/icml-2015/setup.tex
Tweaks
started to clean up introduction

Another common objective in bandit problems is maximising the \emph{cumulative regret}, the total expected reward over all $T$ rounds. 
We have established upper bounds for cumulative regret for parallel bandits but not the general causal bandit case.
Due to space limitations we focus on simple regret and defer these to Appendix~\ref{app:cumulatve}.

@@

In the remainder of this paper we focus on a causal model that is sufficient to demonstrate the separation of regret bounds between algorithms that make use of the additional causal information and those which do not.

>>>>

Another common objective in bandit problems is maximising the \emph{cumulative regret}, the total expected reward over all $T$ rounds. 
We have established upper bounds for cumulative regret for parallel bandits but not the general causal bandit case.
%Due to space limitations we focus on simple regret and defer these to Appendix~\ref{app:cumulatve}.

@@

% In the remainder of this paper we focus on a causal model that is sufficient to demonstrate the separation of regret bounds between algorithms that make use of the additional causal information and those which do not.
